\begin{hcarentry}{SdfMetz}
\report{Tiago Miguel Laureano Alves}%unchanged at least once
\participants{Joost Visser}
\status{stable, maintained}
\makeheader

SdfMetz supports grammar engineering by calculating grammar metrics and other analyses. 
Currently it supports four different grammar formalisms (SDF, DMS, Antlr, and Bison).
The category of supported metrics are size, complexity, structural and disambiguation.
The disambiguation metrics are applicable to the SDF formalism only.
Metrics output is a textual report or in Comma Separated Value format.
The additional analyses implemented are graph visualization of the immediate successor graph, transitive closure graph and strongly-connected components graph outputted in DOT format, and visualization of the non-singleton levels of a grammar.

The definition of all except the ambiguity and the NPath metrics were taken from the paper
\emph{A metrics suite for grammar based-software} by James F.\ Power and Brian A.\ Malloy. 
The ambiguity metrics were defined by the tool author exploiting specific aspects of SDF grammars, and the NPath metric definition was taken from the paper \emph{NPATH: a measure of execution path complexity and its applications}.

The tool was used successfully in a grammar engineering work presented in the paper \emph{A Case Study in Grammar Engineering}.

\FuturePlans
Efforts are underway to develop functionalities to compute quality profiles based on histograms.
Furthermore, more metrics will be added, and a web-interface is planned.

\FinalNote
The tool was initially developed in the context of the IKF-P project (Information Knowledge Fusion, \url{http://ikf.sidereus.pt/}) to develop a grammar for ISO VDM-SL.

\FurtherReading
The web site of SdfMetz
(\url{http://sdfmetz.googlecode.com}) includes the tool source code, and pointers to relevant work about grammar metrication.
\end{hcarentry}
